% -- Encoding UTF-8 without BOM
% -- XeLaTeX => PDF (BIBER)

\documentclass[]{cv-style}          % Add 'print' as an option into the square bracket to remove colours from this template for printing. 
                                    % Add 'espanol' as an option into the square bracket to change the date format of the Last Updated Text

\sethyphenation[variant=british]{english}{} % Add words between the {} to avoid them to be cut 

\begin{document}

\header{Seth M. }{Calkins }           % Your name

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION  -- In the aside, each new line forces a line break
%----------------------------------------------------------------------------------------

\begin{aside}
%
\section{contact}
Noblesville, IN 46060
United States
~
(317) 800 9798
~
sethcalkins@me.com
%
\section{programming}
{\color{red} $\varheartsuit$} R
VBA, SQL, Python
\LaTeX{}
%
\end{aside}
%----------------------------------------------------------------------------------------
% Summary SECTION
%----------------------------------------------------------------------------------------
\vspace{0.2cm}
\section{summary}
  \vspace{-0.2cm}
Visionary strategist with 6+ years of experience leading small to mid-sized businesses in \textbf{increasing revenues, reducing costs, and improving efficiency}. Passionate about leading strategic, transformational technology initiatives that both solve business problems and advance architecture toward desired-state. Keen ability leveraging technology to achieve strategic goals. Innovative and creative problem solver with a passion for implementing process improvement. Solid business acumen, `big picture' perspective, and capacity to exercise sound, independent judgement informed by critical and analytical thinking. Unmistakable professional integrity, unparalleled work ethic, and commitment to excellence.
%----------------------------------------------------------------------------------------
% WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{experience}
  \vspace{-0.2cm}
\begin{entrylist}
%------------------------------------------------
\entry
  {\scalebox{.8}[1.0]{01/2015--Now}}
  {Boré Imprenta e Imagen S.A.}
  {Ciudad Autónoma de Buenos Aires, Argentina}
  {\jobtitle{Diseñador y Diagramador Senior}\\
  En la actualidad soy encargado del Departamento de Diseño y Diagramación, con personal a cargo variable (entre 1 y 3 personas) y trato fluido con los clientes. Ofrecemos soluciones para el diseño de imagen de particulares y pequeñas empresas; diagramación de catálogos, folletos y libros; así como la edición de videos para publicidad y eventos. Trabajando con tecnologías de Adobe Creative Suit (Illustrator/Photoshop/InDesign/Premier Pro/AfterEffects).}
%------------------------------------------ ------
\vspace{-0.3cm}
\entry
  {\scalebox{.8}[1.0]{01/2015--Now}}
  {Oony S.A.}
  {Ciudad Autónoma de Buenos Aires, Argentina}
  {\jobtitle{Desarrollador de Software Junior}\\
  Oony es una Start Up que ofrece una aplicación de Acumulación de Ofertas. Ahí adquirí una amplia batería de conocimientos en \textbf{mantenimiento de servidores} y \textbf{desarrollo de aplicaciones WEB}, tanto back-end como front-end. Específicamente la localización de errores en los servidores (control de Logs y APIs de monitoreo), su solución (desarrollo de mejoras y actualizaciones de software), el desarrollo de la aplicación WEB que concentra una gran cantidad de productos (Scalability); la obtención y el análisis del contenido (Parsing, Data Mining, Classification).\\
  \textbf{Proyectos desarrollados:}
  \begin{itemize}\small{
    \item Parseo de HTML, XML, CSV, JSON (por medio de la biblioteca Scrapy).
    \item Categorización del contenido a partir de sus descripciones\\
    (utilizando las bibliotecas NLTK).
    \item Paralelización de consultas a APIs, optimizando tiempos de respuesta\\
    (manejo de Threads).
    \item Desarrollo de APIs para back-end.}
  \end{itemize}}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	OTHER QUALIFICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{Projects}

\begin{entrylist}
%------------------------------------------------
\entry
{Feb-2015}
{File Manager Application }
{Dharmsinh Desai University}
{Develop File manager Application in android and Register on Google Play Store }
{\vspace{-0.3cm}}
\end{entrylist}

\begin{entrylist}
%------------------------------------------------
\entry
{Jan-2013}
{Social Networking Website}
{VB Polytechnic}
{Develop Social Networking Website on Asp.Net in Aastha Solution, Surat }
{\vspace{-0.3cm}}
\end{entrylist}

\begin{entrylist}
%------------------------------------------------
\entry
{Jan-2013}
{Complete Andruino Project }
{Dharmsinh Desai University}
{Complete Andruino project on Robotics of Sensor }
{\vspace{-0.3cm}}
\end{entrylist}
\begin{entrylist}
%------------------------------------------------
\entry
{Dec-2014}
{Freelancer Website}
{Dharmsinh Desai University}
{Create Freelancer website in ASP.net using SQL Server as 6th semester project}
{\vspace{-0.3cm}}


%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	Achievement  SECTION
%----------------------------------------------------------------------------------------

\section{Achievements}

\begin{entrylist}
%------------------------------------------------
\entry
{}
{ Android App Developer}
{Dharmsinh Desai University}
{Develop File-Manager app in Android using Eclipse Studio and Register on Google Play Store}

%------------------------------------------------
\end{entrylist}
\begin{entrylist}
\entry
{}
{ Start online selling on Different E-commerce Website }
{Dharmsinh Desai University}
{Start firm which sells Fashion wear item on different E-commerce platform like Amazon, Flipkart, Snapdeal ,PayTm etc.}

%------------------------------------------------
\end{entrylist}


\begin{entrylist}
%------------------------------------------------
\entry
{}
{Find New Way to send G-Mail}
{VB Polytechnic}
{Find a new Way to send Mail through SMTP protocol without authentication of Google API.}

\end{entrylist}

\begin{entrylist}
%------------------------------------------------
\entry
{}
{Develop E-commerce Website }
{Dharmsinh Desai University}
{Develop E-Commerce Website for Sweetheart Fashion Pvt Ltd Surat}

\end{entrylist}

\begin{entrylist}
%------------------------------------------------
\entry
{}
{Start Development In IOS }
{Dharmsinh Desai University}
{Register Developer on Freelancer Website (Freelancer.com)}

\end{entrylist}\\\\\

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}
  \vspace{-0.3cm}
\begin{entrylist}
%------------------------------------------------
\entry
{}
{ Developing in JAVA and ASP.Net application:}
{}
{Develop creative application in JAVA as well ASP.net}

\end{entrylist}\
\begin{entrylist}
%------------------------------------------------
\entry
{}
{ CMS Handling}
{}
{Good Knowledge in open-source E-commerce management system like "Odoo"(www.odoo.com) and Orange HRMS live(www.orangehrms.com).}
\end{entrylist}\
\begin{entrylist}
%------------------------------------------------
\entry
{}
{E-commerce Live Problem Solver :}
{}
{Find out Existence problems arise in E-commerce website and give proper solution without any conflict in minimum duration.
}

\end{entrylist}\
%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Skills}
  \vspace{-0.2cm}

\begin{entrylist}
%------------------------------------------------
\entry
  {}
  {Good Management skills}
  {}
  {\jobtitle{}\  Excellent Management Skills which require in company}
%------------------------------------------------
\entry
  {}
  {Programming Ability }
  {}
  {\jobtitle{}\  Good programming skills in C++,JAVA and ASP.NET.}
  
  \entry
  {}
  { Quick Learning Capability}
  {}
  {\jobtitle{}\ Quick learning all the fundamental of the Software Technology    }
  
  \entry
  {}
  {Good in Communication }
  {}
  {\jobtitle{}\  Know five different languages }
  
%------------------------------------------------
%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	Hobby SECTION
%----------------------------------------------------------------------------------------

\section{Hobbies}
  \vspace{-0.2cm}

\begin{entrylist}
%------------------------------------------------

%------------------------------------------------
\entry
  {}
  {Learn abut new Web technology }
  {}
  {\jobtitle{}\ Learn about the latest technology which helpful in company and Improve my
     programming Skills as well.}
  
  \entry
  {}
  {Find Out E-Commerce solution }
  {}
  {\jobtitle{}\ Find out Solution which arise in E-commerce platform on daily base 
  \begin{itemize}
    \item How to fast deliver the product. 
    \item Good Knowledge in CMS data Handling and 'HADOOP' Technology.
     
     
  \end{itemize}}
  \entry
  {}
  {Daily Morning Walk }
  {}
  {\jobtitle{}\ Go morning walk on daily base. }
  \entry
  {}
  {Read Technological Books }
  {}
  {\jobtitle{}\ Like DIGIT , Chip, Ftrack... }
  
%------------------------------------------------
%------------------------------------------------

\end{entrylist}


\end{document}